Publicity Outreach for ``Quantum interval-valued probability: Contextuality and the Born rule''

### 2018-04-14 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling...
etc.~\cite{PironioAcinMassarEtAl2010,MillerShi2016} However, it
is impossible to test randomness directly~\cite{Shi2015}. While
some people believed quantumness implies randomness~\cite{Shi2015,MillerShi2016,Yuan2017},
the randomness of quantum theory cannot be established if we can simulate
quantum theory by a deterministic hidden variable theory. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
theorems exclude any non-local and non-contextuality deterministic
hidden variable theory. However, any physical measurement can only
be done with finite precision, and Meyer~\cite{PhysRevLett.83.3751}
claimed that finite-precision measurements invalidate the spirit of
the Kochen-Specker theorem. In this investigation~\cite{THOS2018},
we employ an interval-valued framework to establish bounds on the
validity of the Kochen-Specker theorem in realistic experimental environments.
In another word, when physical measurements are precise enough, the
Kochen-Specker theorem remains valid, i.e., quantum theory should
not be simulated a non-contextuality deterministic hidden variable
theory. Hence, our results provide additional trust of the randomness
of quantum theory.

>>>>

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling...
etc.~\cite{PironioAcinMassarEtAl2010,MillerShi2016} However, it
is impossible to test randomness directly~\cite{Shi2015}. While
some people believed quantumness implies randomness~\cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the randomness of quantum theory cannot be established if we can simulate
quantum theory by a deterministic hidden variable theory. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,Mermin1990Simple,peres1995quantum,Jaeger2007,Held2016}
theorems exclude any non-local and non-contextuality deterministic
hidden variable theory. However, any physical measurement can only
be done with finite precision, and Meyer~\cite{PhysRevLett.83.3751}
claimed that finite-precision measurements invalidate the spirit of
the Kochen-Specker theorem. In this investigation~\cite{THOS2018},
we employ an interval-valued framework to establish bounds on the
validity of the Kochen-Specker theorem in realistic experimental environments.
In another word, when physical measurements are precise enough, the
Kochen-Specker theorem remains valid, i.e., quantum theory should
not be simulated a non-contextuality deterministic hidden variable
theory. Hence, our results provide additional trust of the randomness
of quantum theory.
